---
title: 'Hello Models: Ames Housing Data'
author: "[Jim Tyhurst, Ph.D.](https://www.jimtyhurst.com/)<br>"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
    hard_line_breaks: FALSE
  html_document:
    toc: true
    code_folding: hide
numbersections: true
vignette: >
  %\VignetteIndexEntry{Hello Models: Ames Housing Data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

## Introduction

The goal of this analysis is to produce a _predictive model_ that predicts the `Sale_Price` of a house, based on other features provided in the data.

This analysis is built from sample code in Kuhn and Silge ([Tidy Modeling with R](https://www.tmwr.org/ames.html). The [tidymodels](https://www.tidymodels.org/) framework is a collection of [packages](https://www.tidymodels.org/packages/) for modeling and machine learning using [tidyverse](https://www.tidyverse.org/) principles.

_Coding style_: Most people do not bother to show the package associated with a function, but I find it easier to learn a new set of packages when each function call is prefixed with the package to which it belongs. For example, `rsample::initial_split`, rather than `initial_split`.

## Exploring the data
First, we load the data:

```{r reads_data, message = FALSE}
library(tidyverse)
library(tidymodels)
library(glmnet)
library(modeldata)
data(ames)

dplyr::glimpse(ames)
```

This data covers five years from `r min(ames$Year_Sold)` to `r max(ames$Year_Sold)`:

```{r year_sold_}
ggplot(ames, aes(x = Year_Sold)) + 
  geom_bar()
```


We want to predict the `Sale_Price`:

```{r sales_price_histogram}
ggplot(ames, aes(x = Sale_Price)) + 
  geom_histogram(bins = 50)
```

We will use the `log` of the `Sales_Price`, so that errors in predicting expensive houses will not have an excessive influence on the model.

```{r sales_price_transformed}
ames_log <- ames %>% mutate(Sale_Price = log10(Sale_Price))
ggplot(ames_log, aes(x = Sale_Price)) + 
  geom_histogram(bins = 50) +
  scale_x_log10()
```

## Splitting the data for training and testing

Split the data into 80% for training and 20% for testing. A stratified random sample will conduct the 80/20 split within each quartile of the data and then pool the results together. This makes it more likely to get a good split of training and test cases, even for the smaller number of very high-priced homes. In {[rsample](https://rsample.tidymodels.org/)}, this is achieved using the `strata` argument with the name of a column:

```{r split}
# Initialize the random number stream, so that the results can be reproduced later. 
set.seed(123)

# Save the split information for an 80/20 split of the data
ames_split <- rsample::initial_split(ames_log, prop = 0.80, strata = Sale_Price)
ames_split
```

## Fitting a model

We will use the [glmnet](https://cran.r-project.org/package=glmnet) package to build a linear regression model. The {[parsnip](https://parsnip.tidymodels.org/)} package provides functions for configuring and fitting a model.

```{r glmnet}
glm_fit <- parsnip::linear_reg(penalty = 1) %>%
  parsnip::set_engine("glmnet") %>%
  parsnip::fit_xy(
    x = rsample::training(ames_split) %>% select(Longitude, Latitude),
    y = rsample::training(ames_split) %>% pull(Sale_Price)
  )
```

Use the `glm_fit` model to make predictions on the test dataset:

```{r glm_predict}
glm_predictions <- predict(
  glm_fit, 
  new_data = 
    rsample::testing(ames_split) |> 
    select(Longitude, Latitude)
)
glm_predictions
```

TODO: Something is wrong ... All of the predicted values are the same value!


```{r min_prediction}
min(glm_predictions$.pred)
```


```{r max_prediction}
max(glm_predictions$.pred)
```

## Source code
[Ames-Housing-Data.Rmd](./Ames-Housing-Data.Rmd)

## References
[Tidymodels](https://www.tidymodels.org/).

[Tidyverse](https://www.tidyverse.org/).

Max Kuhn and Julia Silge. 2021-09-08. [Tidy Modeling with R](https://www.tmwr.org/). Free, online book.
